% filepath: /media/fady/data/cloud/courses/andela_gen-ai-bootcamp/assignments/andela_gen-ai_P4_contract-amendment-extractor/data/test_contracts/amendment.tex
\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{fancyhdr}
\pagestyle{fancy}

\title{\textbf{SERVICE AGREEMENT}}
\author{}
\date{}

\begin{document}
\maketitle

\section*{1. PARTIES}
This Service Agreement (``Agreement'') is entered into as of January 1, 2024, between TechCorp Solutions Inc., a corporation registered in Delaware (``Service Provider''), and ClientCo International Limited, a corporation registered in New York (``Client'').

\section*{2. SERVICES}
Service Provider agrees to provide the following services (``Services''):
\begin{itemize}
  \item Software development and maintenance
  \item Technical support during extended hours (8 AM - 8 PM EST, including weekends)
  \item Quarterly business reviews
  \item Monthly reporting on service metrics
  \item 24/7 emergency hotline support
\end{itemize}

\section*{3. TERM}
This Agreement shall commence on January 1, 2024, and shall continue for a period of twenty-four (24) months (``Initial Term''), unless terminated earlier in accordance with the provisions hereof.

\section*{4. COMPENSATION}
Client shall pay Service Provider a monthly fee of \$65,000 USD, due on the first day of each calendar month. Payment shall be made via wire transfer or ACH to the account designated by Service Provider. An annual cost-of-living adjustment of 3\% shall apply starting Year 2.

\section*{5. CONFIDENTIALITY}
Both parties agree to maintain the confidentiality of all proprietary information disclosed by the other party. This obligation shall survive termination of this Agreement for a period of five (5) years.

\section*{6. LIABILITY}
Service Provider's total liability under this Agreement shall not exceed the fees paid by Client in the twenty-four (24) months preceding the claim. Service Provider shall not be liable for any indirect, incidental, special, or consequential damages. Notwithstanding the foregoing, neither party shall be liable for damages arising from force majeure events.

\section*{7. TERMINATION}
Either party may terminate this Agreement with thirty (30) days' written notice for convenience. Termination for cause may be exercised immediately upon written notice. Upon termination, Service Provider shall deliver all work product and transition services within fifteen (15) days.

\section*{8. INTELLECTUAL PROPERTY}
All work product created by Service Provider under this Agreement shall be owned by Client upon full payment of applicable fees. Service Provider retains the right to use generalized methodologies and pre-existing tools developed prior to this engagement.

\section*{9. GOVERNING LAW}
This Agreement shall be governed by and construed in accordance with the laws of the State of Delaware, without regard to its conflict of law principles. Any disputes shall be resolved through binding arbitration.

\section*{10. ENTIRE AGREEMENT}
This Agreement constitutes the entire agreement between the parties and supersedes all prior negotiations, representations, and agreements, whether written or oral.

\end{document}