% filepath: /media/fady/data/cloud/courses/andela_gen-ai-bootcamp/assignments/andela_gen-ai_P4_contract-amendment-extractor/data/test_contracts/original.tex
\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{fancyhdr}
\pagestyle{fancy}

\title{\textbf{SERVICE AGREEMENT}}
\author{}
\date{}

\begin{document}
\maketitle

\section*{1. PARTIES}
This Service Agreement (``Agreement'') is entered into as of January 1, 2024, between TechCorp Solutions Inc., a corporation registered in Delaware (``Service Provider''), and ClientCo International Limited, a corporation registered in New York (``Client'').

\section*{2. SERVICES}
Service Provider agrees to provide the following services (``Services''):
\begin{itemize}
  \item Software development and maintenance
  \item Technical support during business hours (9 AM - 5 PM EST)
  \item Quarterly business reviews
  \item Monthly reporting on service metrics
\end{itemize}

\section*{3. TERM}
This Agreement shall commence on January 1, 2024, and shall continue for a period of twelve (12) months (``Initial Term''), unless terminated earlier in accordance with the provisions hereof.

\section*{4. COMPENSATION}
Client shall pay Service Provider a monthly fee of \$50,000 USD, due on the first day of each calendar month. Payment shall be made via wire transfer to the account designated by Service Provider.

\section*{5. CONFIDENTIALITY}
Both parties agree to maintain the confidentiality of all proprietary information disclosed by the other party. This obligation shall survive termination of this Agreement for a period of three (3) years.

\section*{6. LIABILITY}
Service Provider's total liability under this Agreement shall not exceed the fees paid by Client in the twelve (12) months preceding the claim. Service Provider shall not be liable for any indirect, incidental, special, or consequential damages.

\section*{7. TERMINATION}
Either party may terminate this Agreement with sixty (60) days' written notice. Upon termination, Service Provider shall deliver all work product and transition services within thirty (30) days.

\section*{8. INTELLECTUAL PROPERTY}
All work product created by Service Provider under this Agreement shall be owned by Client upon full payment of applicable fees.

\section*{9. GOVERNING LAW}
This Agreement shall be governed by and construed in accordance with the laws of the State of Delaware, without regard to its conflict of law principles.

\section*{10. ENTIRE AGREEMENT}
This Agreement constitutes the entire agreement between the parties and supersedes all prior negotiations, representations, and agreements, whether written or oral.

\end{document}