% filepath: /media/fady/data/cloud/courses/andela_gen-ai-bootcamp/assignments/andela_gen-ai_P4_contract-change-extractor/data/test_contracts/02/tex/02_amendment.tex
\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{parskip}

\begin{document}

\begin{center}
\Large\textbf{PROFESSIONAL SERVICES AGREEMENT}
\end{center}

\vspace{0.3cm}

\noindent This Professional Services Agreement (``Agreement'') is entered into as of January 15, 2024 (``Effective Date''), by and between:

\textbf{CLIENT:} TechVision Solutions Inc., a Delaware corporation with its principal place of business at 450 Market Street, San Francisco, CA 94105 (``Client'')

\textbf{CONSULTANT:} DataWorks Consulting LLC, a California limited liability company with its principal place of business at 1200 El Camino Real, Palo Alto, CA 94301 (``Consultant'')

\section*{1. SCOPE OF SERVICES}

Consultant agrees to provide the following professional services (``Services'') to Client:

\subsection*{1.1 Core Services}
Consultant shall provide data analytics consulting services, including but not limited to: (a) development of data warehouse architecture; (b) implementation of ETL pipelines; (c) creation of business intelligence dashboards; (d) training of Client's personnel on analytics tools; and (e) ongoing maintenance and optimization of analytics infrastructure for a period of three (3) months following initial deployment.

\subsection*{1.2 Deliverables}
Consultant shall deliver: (i) comprehensive data architecture documentation within 30 days of project commencement; (ii) fully functional ETL system within 90 days; (iii) interactive dashboards within 120 days; and (iv) monthly performance optimization reports.

\subsection*{1.3 Performance Metrics}
Consultant agrees to meet the following service level objectives: (a) system uptime of 99.5\% during business hours; (b) dashboard load times not exceeding 3 seconds; and (c) data refresh cycles completing within 4-hour windows.

\section*{2. TERM AND TERMINATION}

\subsection*{2.1 Term}
This Agreement shall commence on the Effective Date and continue for a period of nine (9) months, unless earlier terminated as provided herein. The parties may extend this Agreement for additional three (3) month periods upon mutual written consent.

\subsection*{2.2 Termination for Convenience}
Either party may terminate this Agreement upon forty-five (45) days' prior written notice to the other party. Client shall pay for all Services rendered through the effective termination date plus any non-cancellable expenses already incurred.

\subsection*{2.3 Termination for Cause}
Either party may terminate this Agreement immediately upon written notice if the other party materially breaches any provision of this Agreement and fails to cure such breach within fifteen (15) days of receiving written notice thereof.

\section*{3. COMPENSATION}

\subsection*{3.1 Fees}
Client shall pay Consultant a monthly retainer of Eighteen Thousand Dollars (\$18,000.00) for the Services, payable on the first day of each month. Additionally, Client shall pay a performance bonus of Five Thousand Dollars (\$5,000.00) upon successful completion of each major deliverable milestone as defined in Section 1.2.

\subsection*{3.2 Expenses}
Client shall reimburse Consultant for all reasonable and documented out-of-pocket expenses incurred in connection with the performance of the Services, including travel, accommodation, and software licenses, provided such expenses are pre-approved in writing by Client. Monthly expense reimbursements shall not exceed Two Thousand Dollars (\$2,000.00) without additional written authorization.

\subsection*{3.3 Payment Terms}
All invoices shall be paid within fifteen (15) days of receipt. Late payments shall accrue interest at the rate of 1.5\% per month.

\section*{4. INTELLECTUAL PROPERTY}

\subsection*{4.1 Work Product}
All work product, deliverables, inventions, and materials created by Consultant in connection with the Services (``Work Product'') shall be deemed works made for hire and shall be the sole and exclusive property of Client.

\subsection*{4.2 Pre-Existing Materials}
Consultant retains all rights to any pre-existing materials, tools, or methodologies that are not specifically created for Client under this Agreement. Consultant grants Client a perpetual, non-exclusive, royalty-free license to use such pre-existing materials solely in connection with the Work Product.

\subsection*{4.3 Source Code Access}
Consultant shall provide Client with full access to all source code, documentation, and technical specifications related to the Work Product. Such materials shall be delivered in an industry-standard format and shall be sufficiently documented to enable Client's internal team to maintain and modify the systems.

\section*{5. CONFIDENTIALITY}

\subsection*{5.1 Confidential Information}
Each party agrees to hold in confidence all Confidential Information of the other party and shall not disclose such information to any third party without prior written consent. Confidential Information includes, but is not limited to, technical data, business strategies, customer lists, financial information, and proprietary methodologies.

\subsection*{5.2 Exceptions}
Confidential Information does not include information that: (a) is or becomes publicly available through no breach of this Agreement; (b) is rightfully received from a third party; or (c) is required to be disclosed by law.

\section*{6. REPRESENTATIONS AND WARRANTIES}

Consultant represents and warrants that: (a) it has the right and authority to enter into this Agreement; (b) the Services will be performed in a professional and workmanlike manner; and (c) the Work Product will not infringe upon any third-party intellectual property rights.

\section*{7. LIMITATION OF LIABILITY}

In no event shall either party's total liability under this Agreement exceed the total fees paid by Client to Consultant in the six (6) months preceding the claim. Neither party shall be liable for any indirect, incidental, consequential, or punitive damages.

\section*{8. INSURANCE}

Consultant shall maintain professional liability insurance with minimum coverage of Two Million Dollars (\$2,000,000.00) per occurrence and general commercial liability insurance with minimum coverage of One Million Dollars (\$1,000,000.00) per occurrence throughout the term of this Agreement. Consultant shall provide Client with certificates of insurance upon request.

\section*{9. GENERAL PROVISIONS}

\subsection*{9.1 Independent Contractor}
Consultant is an independent contractor and not an employee of Client. Consultant shall be responsible for all taxes and benefits.

\subsection*{9.2 Governing Law}
This Agreement shall be governed by and construed in accordance with the laws of the State of California.

\subsection*{9.3 Entire Agreement}
This Agreement constitutes the entire agreement between the parties and supersedes all prior negotiations and understandings.

\subsection*{9.4 Amendments}
This Agreement may only be amended by a written document signed by both parties.

\vspace{1cm}

\noindent IN WITNESS WHEREOF, the parties have executed this Agreement as of the date first written above.

\vspace{1cm}

\noindent\textbf{CLIENT: TechVision Solutions Inc.}

\vspace{0.5cm}
\noindent By: \underline{\hspace{6cm}} Date: \underline{\hspace{3cm}}

\noindent Name: Sarah Chen

\noindent Title: Chief Technology Officer

\vspace{1cm}

\noindent\textbf{CONSULTANT: DataWorks Consulting LLC}

\vspace{0.5cm}
\noindent By: \underline{\hspace{6cm}} Date: \underline{\hspace{3cm}}

\noindent Name: Michael Rodriguez

\noindent Title: Managing Partner

\end{document}