% filepath: /media/fady/data/cloud/courses/andela_gen-ai-bootcamp/assignments/andela_gen-ai_P4_contract-change-extractor/data/test_contracts/02/tex/02_original.tex
\documentclass[12pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{parskip}

\begin{document}

\begin{center}
\Large\textbf{PROFESSIONAL SERVICES AGREEMENT}
\end{center}

\vspace{0.3cm}

\noindent This Professional Services Agreement (``Agreement'') is entered into as of January 15, 2024 (``Effective Date''), by and between:

\textbf{CLIENT:} TechVision Solutions Inc., a Delaware corporation with its principal place of business at 450 Market Street, San Francisco, CA 94105 (``Client'')

\textbf{CONSULTANT:} DataWorks Consulting LLC, a California limited liability company with its principal place of business at 1200 El Camino Real, Palo Alto, CA 94301 (``Consultant'')

\section*{1. SCOPE OF SERVICES}

Consultant agrees to provide the following professional services (``Services'') to Client:

\subsection*{1.1 Core Services}
Consultant shall provide data analytics consulting services, including but not limited to: (a) development of data warehouse architecture; (b) implementation of ETL pipelines; (c) creation of business intelligence dashboards; and (d) training of Client's personnel on analytics tools.

\subsection*{1.2 Deliverables}
Consultant shall deliver: (i) comprehensive data architecture documentation within 30 days of project commencement; (ii) fully functional ETL system within 90 days; and (iii) interactive dashboards within 120 days.

\section*{2. TERM AND TERMINATION}

\subsection*{2.1 Term}
This Agreement shall commence on the Effective Date and continue for a period of six (6) months, unless earlier terminated as provided herein.

\subsection*{2.2 Termination for Convenience}
Either party may terminate this Agreement upon thirty (30) days' prior written notice to the other party.

\subsection*{2.3 Termination for Cause}
Either party may terminate this Agreement immediately upon written notice if the other party materially breaches any provision of this Agreement and fails to cure such breach within fifteen (15) days of receiving written notice thereof.

\section*{3. COMPENSATION}

\subsection*{3.1 Fees}
Client shall pay Consultant a monthly retainer of Fifteen Thousand Dollars (\$15,000.00) for the Services, payable on the first day of each month.

\subsection*{3.2 Expenses}
Client shall reimburse Consultant for all reasonable and documented out-of-pocket expenses incurred in connection with the performance of the Services, including travel, accommodation, and software licenses, provided such expenses are pre-approved in writing by Client.

\subsection*{3.3 Payment Terms}
All invoices shall be paid within thirty (30) days of receipt. Late payments shall accrue interest at the rate of 1.5\% per month.

\section*{4. INTELLECTUAL PROPERTY}

\subsection*{4.1 Work Product}
All work product, deliverables, inventions, and materials created by Consultant in connection with the Services (``Work Product'') shall be deemed works made for hire and shall be the sole and exclusive property of Client.

\subsection*{4.2 Pre-Existing Materials}
Consultant retains all rights to any pre-existing materials, tools, or methodologies that are not specifically created for Client under this Agreement.

\section*{5. CONFIDENTIALITY}

\subsection*{5.1 Confidential Information}
Each party agrees to hold in confidence all Confidential Information of the other party and shall not disclose such information to any third party without prior written consent.

\subsection*{5.2 Exceptions}
Confidential Information does not include information that: (a) is or becomes publicly available through no breach of this Agreement; (b) is rightfully received from a third party; or (c) is required to be disclosed by law.

\section*{6. REPRESENTATIONS AND WARRANTIES}

Consultant represents and warrants that: (a) it has the right and authority to enter into this Agreement; (b) the Services will be performed in a professional and workmanlike manner; and (c) the Work Product will not infringe upon any third-party intellectual property rights.

\section*{7. LIMITATION OF LIABILITY}

In no event shall either party's total liability under this Agreement exceed the total fees paid by Client to Consultant in the six (6) months preceding the claim. Neither party shall be liable for any indirect, incidental, consequential, or punitive damages.

\section*{8. GENERAL PROVISIONS}

\subsection*{8.1 Independent Contractor}
Consultant is an independent contractor and not an employee of Client. Consultant shall be responsible for all taxes and benefits.

\subsection*{8.2 Governing Law}
This Agreement shall be governed by and construed in accordance with the laws of the State of California.

\subsection*{8.3 Entire Agreement}
This Agreement constitutes the entire agreement between the parties and supersedes all prior negotiations and understandings.

\subsection*{8.4 Amendments}
This Agreement may only be amended by a written document signed by both parties.

\vspace{1cm}

\noindent IN WITNESS WHEREOF, the parties have executed this Agreement as of the date first written above.

\vspace{1cm}

\noindent\textbf{CLIENT: TechVision Solutions Inc.}

\vspace{0.5cm}
\noindent By: \underline{\hspace{6cm}} Date: \underline{\hspace{3cm}}

\noindent Name: Sarah Chen

\noindent Title: Chief Technology Officer

\vspace{1cm}

\noindent\textbf{CONSULTANT: DataWorks Consulting LLC}

\vspace{0.5cm}
\noindent By: \underline{\hspace{6cm}} Date: \underline{\hspace{3cm}}

\noindent Name: Michael Rodriguez

\noindent Title: Managing Partner

\end{document}